BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-11-20 LabelStyles/SoS-skeleton-Det.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
`r writer_fide(data)`
\endgroup

\vspace*{\fill}
\begingroup
`r data$Gen`. `r writer(data$Site)` `r data$latitude_dd` `r data$longitude_dd` (`r data$Datum` `r writer(data$Coordinate_uncertainty)`).

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

\vspace*{\fill}
\begingroup
`r collection_writer(data)`.
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

\begin{center}
\textbf{\LARGE `r record[['Project_name']]`}
\end{center}
\vspace{-\baselineskip} 
\uppercase{`r record[['Family']]`}  
\vspace{-\baselineskip} 
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\normalsize 
`r writer_fide(record)`
\endgroup

\vspace{\fill}
\begingroup
\small
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record$Habitat)`. `r record[['physical_environ']]`

Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\par\vspace{\fill}

\begingroup
\small
`r collection_writer(record)`
\endgroup

\vspace{-\baselineskip} 
\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-11-20 LabelStyles/SoS-skeleton-Spaced.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
\endgroup

\vspace*{\fill}
\begingroup
`r data$Gen`. `r writer(data$Site)` `r data$latitude_dd` `r data$longitude_dd` (`r data$Datum` `r writer(data$Coordinate_uncertainty)`).

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

\vspace*{\fill}
\begingroup
`r collection_writer(data)`. `r writer_fide(data)`
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

\begin{center}
\textbf{\LARGE `r record[['Project_name']]`}
\end{center}
\vspace{-\baselineskip} 
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}
\vspace{-\baselineskip} 
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\endgroup

\vspace{\fill}
\begingroup
\small
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record$Habitat)`. `r record[['physical_environ']]`

Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\par\vspace{\fill}

\begingroup
\small
`r collection_writer(record)`. `r writer_fide(record)`
\endgroup

\vspace{-\baselineskip} 
\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-11-20 LabelStyles/SoS-skeleton-familyLeft.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE `r data$Project_name`}
\end{center}
\large
\uppercase{`r data$Family`}  
\begingroup
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\endgroup
\normalsize

\vspace*{\fill}
\begingroup
`r data$Gen`. `r writer(data$Site)` `r data$latitude_dd` `r data$longitude_dd` (`r data$Datum` `r writer(data$Coordinate_uncertainty)`).

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

\vspace*{\fill}
\begingroup
`r collection_writer(data)`. `r writer_fide(data)`
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)  |>
  dplyr::mutate(Project_name = 'SOS Template')
```

\begin{center}
\textbf{\LARGE `r record[['Project_name']]`}
\end{center}
\vspace{-\baselineskip} 
\uppercase{`r record[['Family']]`}  
\vspace{-\baselineskip} 
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\endgroup

\vspace{\fill}
\begingroup
\small
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record$Habitat)`. `r record[['physical_environ']]`

Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\par\vspace{\fill}

\begingroup
\small
`r collection_writer(record)`. `r writer_fide(record)`
\endgroup

\vspace{-\baselineskip} 
\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-11-20 LabelStyles/SoS-skeleton-large.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\large Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
\endgroup

\vspace*{\fill}
\begingroup
`r data$Gen`. `r writer(data$Site)` `r data$latitude_dd` `r data$longitude_dd` (`r data$Datum` `r writer(data$Coordinate_uncertainty)`).

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

\vspace*{\fill}
\begingroup
`r collection_writer(data)`. `r writer_fide(data)`
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

\begin{center}
\textbf{\large `r record[['Project_name']]`}
\end{center}
\vspace{-\baselineskip} 
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}
\vspace{-\baselineskip} 
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\endgroup

\vspace{\fill}
\begingroup
\small
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record$Habitat)`. `r record[['physical_environ']]`

Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\par\vspace{\fill}

\begingroup
\small
`r collection_writer(record)`. `r writer_fide(record)`
\endgroup

\vspace{-\baselineskip} 
\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-11-20 LabelStyles/SoS-skeleton-noDet.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

>>>>

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

### 2025-11-20 LabelStyles/SoS-skeleton-noDir.Rmd
resubmitted version

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
\endgroup

\vspace*{\fill}
\begingroup
`r data$Gen`. `r writer(data$Site)` `r data$latitude_dd` `r data$longitude_dd` (`r data$Datum` `r writer(data$Coordinate_Uncertainty)`).

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

\vspace*{\fill}
\begingroup
`r collection_writer(data)`. `r writer_fide(data)`
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

\begin{center}
\textbf{\LARGE `r record[['Project_name']]`}
\end{center}
\vspace{-\baselineskip} 
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}
\vspace{-\baselineskip} 
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\endgroup

\vspace{\fill}
\begingroup
\small
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record$Habitat)`. `r record[['physical_environ']]`  
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\par\vspace{\fill}

\begingroup
\small
`r collection_writer(record)`. `r writer_fide(record)`
\endgroup

\vspace{-\baselineskip} 
\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-11-20 LabelStyles/skeleton-SOS.Rmd
resubmitted version

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

@@

`r writer(record$Habitat)`. `r record[['physical_environ']]`  
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

>>>>

```{r load data}
record <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'SOS Template')
```

@@

`r writer(record$Habitat)`. `r record[['physical_environ']]`  
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup
\begingroup
\begin{spacing}{0.02}
{\scriptsize `r record[['Directions_BL']]`}
\end{spacing}
\endgroup

### 2025-11-20 LabelStyles/skeleton-customfont-downloaded.Rmd
resubmitted version

---
output: 
  pdf_document:
    latex_engine: xelatex # or lualatex
    keep_tex: true
params:
  Collection_number: NULL
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
  - \usepackage{wrapfig}
---

@@

```{r load library, eval = T}
library(BarnebyLives)

local <- file.path(path.expand('~'), 'Documents', 'assoRted', 'Barneby_Lives_dev', 'LabelStyles')
logopath <- file.path(local, 'logo.png')

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |> # default feed in the path to your csv. 
  dplyr::filter(Collection_number == params$Collection_number) |>  
  sf::st_drop_geometry() |>
  dplyr::mutate(Project_name = 'Logos', Coordinate_uncertainty = ' +/- 5m')

# escape character columns to ensure characters which interfere with latex
# rendering are escaped. 
char_cols <- sapply(record, is.character)
char_col_names <- names(record)[char_cols]
record[char_col_names] <- lapply(record[char_col_names], escape_latex)
```

\begin{center}
\textbf{\Large `r writer(record[['Project_name']])`}
\end{center}
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}

\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)`  `r writer(record[['Infraspecific_authority']])`
\normalsize
\endgroup

\vspace{\fill}

\begingroup
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record[['Habitat']])`. `r record[['physical_environ']]` \par
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\vspace{\fill}

\noindent
\begin{minipage}[t]{0.75\textwidth}
  \begingroup 
  `r collection_writer(record)`
  `r writer_fide(record)`
  \endgroup
\end{minipage}
\hfill
\begin{minipage}[b]{0.2\textwidth}
  \includegraphics[width=\linewidth,keepaspectratio]{`r logopath`}
\end{minipage}

>>>>

---
output: 
  pdf_document:
    latex_engine: xelatex # or lualatex
    keep_tex: true
params:
  Collection_number: Collection_number
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - |
    \setmainfont[
      Path = /home/sagesteppe/Documents/assoRted/Barneby_Lives_dev/LabelStyles/Nunito/static/,
      UprightFont = *-Regular,
      ItalicFont = *-Italic,
      BoldFont = *-Bold,
      BoldItalicFont = *-BoldItalic
    ]{Nunito}
---

@@

```{r load library}
library(BarnebyLives)
```

```{r load data}
local <- file.path('~', 'Documents', 'assoRted', 'Barneby_Lives_dev', 'LabelStyles')

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  dplyr::filter(Collection_number == params$Collection_number)  |>
  dplyr::mutate(Project_name = 'Custom font downloaded')
```

\begin{center}
\textbf{\Large `r writer(record[['Project_name']])`}
\end{center}
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
\normalsize
\endgroup

\vspace{\fill}
\begingroup
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

`r writer(record[['Habitat']])`. `r record[['physical_environ']]` \par
Vegetation: `r species_font(record[['Vegetation']])` \par
`r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

\vspace{\fill}
\begingroup
`r collection_writer(record)` \par
`r writer_fide(record)`
\endgroup

### 2025-11-20 LabelStyles/skeleton-customfont-twofonts.Rmd
resubmitted version

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number) 
```

>>>>

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number)  |>
  dplyr::mutate(Project_name = 'Custom font - two of them')
```

### 2025-11-20 LabelStyles/skeleton-customfont.Rmd
resubmitted version

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number) 
```

>>>>

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number)  |>
  dplyr::mutate(Project_name = 'Custom font Skeleton')
```

### 2025-11-20 LabelStyles/skeleton-default.Rmd
resubmitted version

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number)

>>>>

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number) |>
  dplyr::mutate(Project_name = 'Default Template')

### 2025-11-20 LabelStyles/skeleton-modern.Rmd
resubmitted version

\vspace{\fill}
\begingroup
`r record[['Gen']]`. `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).  `r writer(record[['Site']])`

`r writer(record[['Habitat']])`. `r record[['physical_environ']]`  
Vegetation: `r species_font(record[['Vegetation']])` 
`r associates_writer(record[['Associates']], full = TRUE)` 
`r writer(record[['Notes']])`  
\endgroup

\vspace{\fill}
\begingroup
`r collection_writer(record)`.  
`r writer_fide(record)`
\endgroup

>>>>

\vspace{\fill}

\begingroup
`r record[['Gen']]`. `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).  `r writer(record[['Site']])` 
\endgroup

\vspace{\fill}

\begingroup
`r writer(record[['Habitat']])`. `r record[['physical_environ']]` 
\endgroup

\vspace{\fill}

\begingroup
Vegetation: `r species_font(record[['Vegetation']])` \newline 
`r associates_writer(record[['Associates']], full = TRUE)` \newline 
`r writer(record[['Notes']])`  
\endgroup

\vspace{\fill}

\begingroup
`r collection_writer(record)`.  
`r writer_fide(record)`
\endgroup

### 2025-11-20 manuscript/Appendices.Rmd
resubmitted version

# Appendix A: System Information for Benchmarking

@@

Architecture:             x86_64  
  CPU op-mode(s):         32-bit, 64-bit  
  Address sizes:          39 bits physical, 48 bits virtual  
  Byte Order:             Little Endian  
CPU(s):                   16  
  On-line CPU(s) list:    0-15  
Vendor ID:                GenuineIntel  
  Model name:             11th Gen Intel(R) Core(TM) i7-11700K @ 3.60GHz  
    CPU family:           6  
    Model:                167  
    Thread(s) per core:   2  
    Core(s) per socket:   8  
    Socket(s):            1  
    Stepping:             1  
    CPU max MHz:          5100.0000  
    CPU min MHz:          800.0000  
    BogoMIPS:             7200.00

@@

```{sh, eval = F}
free -h
```
               total        used        free      shared  buff/cache   available  
Mem:           125Gi       3.1Gi       112Gi       569Mi       9.7Gi       120Gi  
Swap:          2.0Gi          0B       2.0Gi

@@

Filesystem      Size  Used Avail Use% Mounted on  
tmpfs            13G  2.6M   13G   1% /run  
/dev/nvme0n1p2  468G  242G  203G  55% /  
tmpfs            63G   14M   63G   1% /dev/shm  
tmpfs           5.0M  4.0K  5.0M   1% /run/lock  
efivarfs        192K   88K  100K  47% /sys/firmware/efi/efivars  
/dev/nvme0n1p1  511M  6.1M  505M   2% /boot/efi  
tmpfs            13G  132K   13G   1% /run/user/1000  
/dev/sda1       3.6T  3.2T  295G  92% /media/steppe/hdd

@@

>>>>

---
output:
  pdf_document: default
---
# Appendix 1: System Information for Benchmarking

@@

| Field               | Value                                          |
| ------------------- | ---------------------------------------------- |
| Architecture        | x86_64                                         |
| CPU op-mode(s)      | 32-bit, 64-bit                                 |
| Address sizes       | 39 bits physical, 48 bits virtual              |
| Byte Order          | Little Endian                                  |
| CPU(s)              | 16                                             |
| On-line CPU(s) list | 0-15                                           |
| Vendor ID           | GenuineIntel                                   |
| Model name          | 11th Gen Intel(R) Core(TM) i7-11700K @ 3.60GHz |
| CPU family          | 6                                              |
| Model               | 167                                            |
| Thread(s) per core  | 2                                              |
| Core(s) per socket  | 8                                              |
| Socket(s)           | 1                                              |
| Stepping            | 1                                              |
| CPU max MHz         | 5100.0000                                      |
| CPU min MHz         | 800.0000                                       |
| BogoMIPS            | 7200.00                                        |

\newpage

@@

```{sh, eval = F}
free -h
```

| Type | Total | Used  | Free  | Shared | Buff/Cache | Available |
| ---- | ----- | ----- | ----- | ------ | ---------- | --------- |
| Mem  | 125Gi | 3.1Gi | 112Gi | 569Mi  | 9.7Gi      | 120Gi     |
| Swap | 2.0Gi | 0B    | 2.0Gi | —      | —          | —         |

@@

| Filesystem     | Size | Used | Avail | Use% | Mounted on                |
| -------------- | ---- | ---- | ----- | ---- | ------------------------- |
| tmpfs          | 13G  | 2.6M | 13G   | 1%   | /run                      |
| /dev/nvme0n1p2 | 468G | 242G | 203G  | 55%  | /                         |
| tmpfs          | 63G  | 14M  | 63G   | 1%   | /dev/shm                  |
| tmpfs          | 5.0M | 4.0K | 5.0M  | 1%   | /run/lock                 |
| efivarfs       | 192K | 88K  | 100K  | 47%  | /sys/firmware/efi/efivars |
| /dev/nvme0n1p1 | 511M | 6.1M | 505M  | 2%   | /boot/efi                 |
| tmpfs          | 13G  | 132K | 13G   | 1%   | /run/user/1000            |
| /dev/sda1      | 3.6T | 3.2T | 295G  | 92%  | /media/steppe/hdd         |

@@

\newpage

# Appendix 2: Label Templates

\begin{center}
\includegraphics[width=420pt]{./labels/TemplateExamples.png}
\end{center}
